Relict deciduous oaks show high resilience to drought despite the effect of land-use legacies

### 2019-07-10 man/tables/t_dendro_summary.Rmd
table update

---
output:
  word_document:
    reference_docx: ../../templates/template_tables_portrait.docx
bibliography: ../../refs/references.bib
csl: ../../refs/ecology.csl
editor_options: 
  chunk_output_type: console
---

>>>>

---
output:
  word_document:
    reference_docx: ../../templates/template_tables_portrait.docx
bibliography: ../../refs/references.bib
csl: ../../refs/ecosystems.csl
editor_options: 
  chunk_output_type: console
---

### 2019-07-10 man/tables/t_droughts.Rmd
update
table update

---
output:
  word_document:
    reference_docx: ../../templates/template_tables_portrait.docx
bibliography: ../../refs/references.bib
csl: ../../refs/ecology.csl
---

@@

##### 
**Table S3.** Drought events for Sierra Nevada based on SPEI index (12 months scale). See methods for details.

>>>>

---
output:
  word_document:
    reference_docx: ../../templates/template_tables_portrait.docx
bibliography: ../../refs/references.bib
csl: ../../refs/ecosystems.csl
---

@@

##### 
**Table S3.** Drought events for the 1901-2016 period for Sierra Nevada based on SPEI index (12 months scale). See methods for details.

### 2019-07-10 man/tables/t_forest_history.Rmd
table update

---
output:
  word_document:
    reference_docx: ../../templates/template_tables_portrait.docx
bibliography: ../../refs/references.bib
csl: ../../refs/ecology.csl
---

@@

```{r}
library(tidyverse)
library(here)
library(pander)
library(kableExtra)
library(knitr)
library(dplyr)
library(flextable)
library(officer)
```

**Table S3.** Review of the foorest and management history of the sampling sites

In addition, the forest and managment history of our sampling sites was inferred from a detailed analysis of historical land-use changes. For this purpose, an exhaustive review of historical documents was done to compile information about socio-economical activities affecting forest Table XX

$ convertir en tabla $ 
: land-uses, forest managment actions, mining, wildfires, etc. Several documentary sources were reviewed: historical documents and maps [*e.g.* @Titos1990]; detailed mining reports [*e.g.* @Maestre1858]; official information about recent wildfires events and forest management practices [@Bonet2016obsnev_forest]; livestock farming [*e.g.* @MorenoLlorca2016]; traditional irrigation ditches [@RuizRuiz2017] and other studies reviewing the socioeconomic dynamics of forest of Sierra Nevada at different scales [@JimenezOlivencia2015; @MorenoLlorca2016].

```{r, eval=FALSE}
### Table R1_evi
evi <- read.csv(here("/out/anovas_resilience/huber_evi", "trimmed_anovas.csv"), header = TRUE)
names(evi) <- c('factores', 'F', 'p', 'variables')

dff_evi <- evi %>% gather(temp, numeros, F, p) %>% 
  unite(temp1, variables, temp) %>% 
  spread(temp1, numeros) %>% 
  mutate(factores = recode(factores, 
                           "disturb_year" = "Drought event", 
                           "disturb_year:site" = "Drought event:Site", 
                           "site" = "Site")) %>% 
  arrange(match(factores, c("Drought event", "Site", "Drought event:Site"))) %>% 
  mutate_at(c(2,4,6,8), round, 1) %>% 
  mutate_at(c(3,5,7,9), round, 3) %>% 
  mutate(variable = 'EVI')

bai <- read.csv(here("/out/anovas_resilience/huber_bai", "trimmed_anovas.csv"), header = TRUE)
names(bai) <- c('factores', 'F', 'p', 'variables')

dff_bai <- bai %>% gather(temp, numeros, F, p) %>% 
  unite(temp1, variables, temp) %>% 
  spread(temp1, numeros) %>% 
  mutate(factores = recode(factores, 
                           "disturb_year" = "Drought event", 
                           "disturb_year:site" = "Drought event*Site", 
                           "site" = "Site")) %>% 
  arrange(match(factores, c("Drought event", "Site", "Drought event*Site"))) %>% 
  mutate_at(c(2,4,6,8), round, 1) %>% 
  mutate_at(c(3,5,7,9), round, 3) %>% 
  mutate(variable = 'BAI')

dff <- dff_evi %>% 
  bind_rows(dff_bai) %>% 
  dplyr::select(-rrs_F, -rrs_p) %>% 
  dplyr::select(variable, factores, rt_F, rt_p, rc_F, rc_p, rs_F, rs_p)
```

```{r, eval = FALSE}
mt <- regulartable(
  data = dff, 
  col_keys = c("variable", "factores", "c3","rt_F", "rt_p", "c1", "rc_F", "rc_p","c2", "rs_F", "rs_p"),
)

mti <- mt %>% 
  autofit() %>% 
  empty_blanks() %>% 
  align(j = 1,  align = "center") %>% 
  merge_v(~variable) %>% 
  set_header_labels(variable = "", factores = "", rt_F = "Resistance", rt_p = "Resistance", rc_F = "Recovery", rc_p = "Recovery", rs_F = "Resilience", rs_p = "Resilience") %>% 
  add_header(variable = "Variable", factores = "Factor", rt_F = "F", rt_p = "p", rc_F = "F", rc_p = "p", rs_F = "F", rs_p = "p", top = FALSE) %>% 
  bold(part = 'header') %>% 
  fontsize(part = "header", size = 10) %>%
  fontsize(part = "body", size = 9) %>% 
  width(j = 2, width = 2) %>% 
  italic(i = ~ rt_p < 0.01, j = ~ rt_p) %>% 
  italic(i = ~ rc_p < 0.01, j = ~ rc_p) %>% 
  italic(i = ~ rs_p < 0.01, j = ~ rs_p) %>% 
  merge_at(i = 1, j=4:5, part="header") %>% 
  merge_at(i = 1, j=7:8, part="header") %>% 
  merge_at(i = 1, j=10:11, part="header")

mti
# mt <- set_formatter(mt, 
#                     rt_F = function(x) format(round(x, 1)),
#                     rc_F = function(x) format(round(x, 1)),
#                     rs_F = function(x) format(round(x, 1))
#                     ) 
# 
# mt

```

>>>>

---
output:
  word_document:
    reference_docx: ../../templates/template_tables_portrait.docx
bibliography: ../../refs/references.bib
csl: ../../refs/ecosystems.csl
editor_options: 
  chunk_output_type: console
---

@@

```{r}
library(tidyverse)
library(here)
library(pander)
library(kableExtra)
library(knitr)
library(dplyr)
library(flextable)
library(officer)
library(tidyverse)
```

**Table S4.** Review of the forest and management history of the samplin site. An exhaustive review of historical documents was done to compile information about socio-economical activities affecting forest. Several documentary sources were reviewed: historical documents and maps [*e.g.* @Titos1990]; detailed mining reports [*e.g.* @Maestre1858]; official information about recent wildfires events and forest management practices [@Bonet2016obsnev_forest]; livestock farming [*e.g.* @MorenoLlorca2016]; traditional irrigation ditches [@RuizRuiz2017] and other studies reviewing the socioeconomic dynamics of forest of Sierra Nevada at different scales [@JimenezOlivencia2015; @MorenoLlorca2016].

[@Catastro1752; @Lopez1776; @Madoz1846; @Maestre1852; @Maestre1858; @Cruz1991; @Titos1990; @Titos1997; @Ferrer1999; @MesaTorres2009; @Bonet2014_conama; @Navarro2014; @MartinCivantos2014; @MartinMontanes2015; @JimenezOlivencia2015; @2015Zoido; @Wing2015; @Bonet2016obsnev_forest; @MorenoLlorca2016; @RuizRuiz2017; @CMA2018; @Calatrava2019; J. Navarro and F.J. Cano-Manuel *personal communications*]

@Catastro1752; @MesaTorres2009; @Bonet2014_conama
@Bonet2014_conama; @MorenoLlorca2016; @CMA2018
@Bonet2016obsnev_forest; @MorenoLlorca2016; J. Navarro and F.J. Cano-Manuel *personal communications*
@Cruz1991; @Wing2015
@JimenezOlivencia2015; @2015Zoido; @MorenoLlorca2016; @Calatrava2019
@Maestre1852; @Maestre1858; @Titos1990; @MesaTorres2009
@Navarro2014
@MartinCivantos2014; @MartinMontanes2015; @RuizRuiz2017
@Catastro1752; @Lopez1776; @Madoz1846; @Titos1997; @Ferrer1999; @MesaTorres2009; @Bonet2014_conama

```{r}
u_raw <- read_delim(here::here("/data_raw/review_usos.tsv"), delim = "\t") %>% 
  dplyr::select(-ref) %>% spread(Site, item)

u <- regulartable(u_raw, 
                   col_keys = c("activity", "CA", "SJ", "refall"))

tabla <- u %>% 
  set_header_labels(activity = "", CA = "Cáñar (CA sites)", SJ = "Güejar-Sierra (SJ site)", refall = "References") %>% 
  bold(part = "header") %>% 
  bold(j = 1) %>% 
  border_outer(part = "all", border = fp_border(color = "black", width = 1.5)) %>% 
  border_inner_h(part="all", border = fp_border(color = "gray")) %>% 
  border_inner_v(part="all", border = fp_border(color = "gray")) %>% 
  fontsize(part = "header", size = 10) %>% 
  fontsize(part = "body", size = 9) %>% 
  autofit(add_w = 0, add_h = 0)

tabla 
```
